A Realistic Guide to Making Data Available Alongside Code to Improve Reproducibility

### 2019-06-28 paper.Rmd
Added Binder reference

The computing environment is also easily captured with modern tools such as Docker [@Boettiger2015; @Jupyter2018]. Modern tools such as Binder (citation) can parse Docker files and dependency trees to provide on demand, live notebooks in R and Python that a reader can immediately execute in the browser without dealing with the challenges of local installation. This makes it simple to load a specific environment to run any analysis. Code is handled by version control with tools like Git and GitHub [@git; @github], paired with archiving such as Zenodo provide access to code (particularly model implementations)[@zenodo]. All the necessary software is available from various package managers (and their numerous geographic mirrors and archives) making it easy to install any version of a software package. However, the biggest challenge, even today, remains easy and repeatable access to data in a data analysis.

>>>>

The computing environment is also easily captured with modern tools such as Docker [@Boettiger2015; @Jupyter2018]. Modern tools such as Binder [@Jupyter2018] can parse Docker files and dependency trees to provide on demand, live notebooks in R and Python that a reader can immediately execute in the browser without dealing with the challenges of local installation. This makes it simple to load a specific environment to run any analysis. Code is handled by version control with tools like Git and GitHub [@git; @github], paired with archiving such as Zenodo provide access to code (particularly model implementations)[@zenodo]. All the necessary software is available from various package managers (and their numerous geographic mirrors and archives) making it easy to install any version of a software package. However, the biggest challenge, even today, remains easy and repeatable access to data in a data analysis.
